\section*{Introduction}
In computer science, an agent is a software who works autonomous. It acts like an automaton according to how it was developped.\\
 It's a kind of artificial intelligence.\\
  An agent can be :\\
\begin{itemize}
	\item Reactive: It can act regarding to his environment.
	\item Proactive: It can take initiative to reach its goal.
	\item "Sociable": It can communicate with other agents.
\end{itemize}
Agent can be use in many fields, for example it there is an agent to organize import and export of containers in a container terminal at Göteborg,this agent permits to fill, empty and stack containers from ships in the dock via machines. Machine moving are managed by agents and are optimized to be the quickest as possible.\\
An other example very much simple is just a reactive agent which can sent automatic responses when you order a command or something else.\\
So, agent are usefull to do some tasks and can make the life easier.\\
The TAC agent competition is an international forum designed to promote and encourage high quality research into the trading agent problem.\\
In the TAC classic, we are an agent reponsible of 8 clients who want to go in holliday. We have to create travel packages to answer to their preferences (Flight date, Hotel preferences, Entertainements asked).\\
We have to participate to different auctions to make the packages. There are 3 different auctions:\\
\begin{itemize}
\item Flight auctions
\item Hotel auctions
\item Entertainement auctions
\end{itemize}
We will describe each of behaviour auction in the rest of this report.\\
We will participate to a competition between each agents of the different group of student.\\
At the end of the competion we will have a score regarding our holding and the higher score will win.\\
So we have to design an agent to win this competition, this report will describe how we've developped our agent.
