\section{Strategies}

\subsection{Flight strategy}

For the hotel auction strategy, we've decided to put 2 limits:\\
\begin{itemize}
\item A low limit: if the price of the hotel that we want goes under this limit, we buy it.
\item A high limit: if the price become too high and goes over this limit we buy it too, to prevent a too big spending.
\end{itemize}
At the begining we just put a low limit, but after many tests, we saw that the price usually become really big after some times then, we decided to put a high limit.
In a first step we've put some fixed limits (200 for the low limit and 400 for the high limit) but after thought, we realized that was not really relevant because the prices begin between 250 and 400 so there can be a gap between some auction.\\
So we decided to adapt the limits for each auction. We've put different limits for the each auctions, regarding the starting price of the auction:\\
\begin{itemize}
\item Low limit = Starting price - 10% of the starting price
\item High limit = Starting price + 10% of the starting price
\end{itemize}
This is a better strategy than before because we adapt our price according to each auction and not only a global strat for all the auctions.

\subsection{Hotel strategy}

For the hotel strategy, it's a bit more complicated than the flight one.\\
As these auctions are english auction, we thought that we have to put a enough big price to get ou hotel but not to big to not make the price grow too much.\\
So this strategy is based on a variable "delta". This delta is the average ask price changes, each time the auction change, we update the delta by this function: delta= (delta + newAskPrice - oldAskPrice)/2. With the function we can have an overview of what will happen in the future rounds.\\
Each time the quote for the auction is update, we compared the ask price with our bid and then there is 2 possibility:\\
\begin{itemize}
\item The ask price is higher than our bid, in that case we change our bid price for the ask price+delta.
\item The ask price is lower than our bid in that case we change nothing
\end{itemize}
This strategy permits to have a bigger price than the ask price because each time the ask price go over our bid we update it. And it permits to not have a too big price because if our price is higher than the ask price we don't update our bid.\\
Updating with the delta permits to  predict the future growth of the price and allow us to not update our price each time there is a new ask price but just in case we will not have the hotel.

\subsection{Entertainement strategy}
