\section*{Introduction}
In computer science, an agent is a software who works autonomously. It acts like an automaton according to how it was developped.\\
 It's a kind of artificial intelligence.\\
  An agent can be :\\
\begin{itemize}
	\item Reactive: It can act regarding to his environment.
	\item Proactive: It can take initiative to reach its goal.
	\item "Sociable": It can communicate with other agents.
\end{itemize}
Agents can be use in many fields, for example there is an agent who organize import and export of containers in a container terminal at Göteborg, this agent permits to fill, empty and stack containers from ships to the docks via machines. Machine moving are managed by agents and are optimized to be the quickest as possible.\\
Another example very simple is just a reactive agent which can send automatic responses when one orders a command or something else.\\
So, agent are useful to do some tasks and can make the life easier.\\
The TAC agent competition is an international forum designed to promote and encourage high quality research into the trading agent problem.\\
In the TAC classic, we are an agent reponsible of 8 clients who want to go in holidays. We have to create travel packages to answer to their preferences (Flight date, Hotel preferences, Entertainements asked).\\
We have to participate to different auctions to make the packages. There are 3 different auctions:\\
\begin{itemize}
\item Flight auctions
\item Hotel auctions
\item Entertainement auctions
\end{itemize}
We will describe the behaviour of each auction in the rest of this report.\\
We will participate to a competition between each agent of the different group of student.\\
At the end of the competion we will have a score regarding our holdings and the higher score will win.\\
So we have to design an agent to win this competition, this report will describe how we've developped our agent.
