\section{Results}

The first result that jumped to our eyes was the score : we ended up in all the game with a negative score, revealing unsatisfaction of our clients.

\subsection{Flight}
This part of the game went smoothly : our strategy allowed us to limit the price at which we buy the flights, and it resulted in a moderate price at the end.\\
Furthermore, we have not even once disappointed our clients : we have had at all time all the fights wanted.\\
Thus, we believe our strategy to be suited for the TAC game.

\subsection{Hotel}
This part is more complicated. In two games out of three, we didn't get one hotel night for several clients.\\
The results were numerous infeasible packages (4 or 5 out of 8) and a huge drop in client's satisfaction.\\
This problem can come from a problem with our implementation or with the communication to the server, however we've not been able to pinpoint it.
The second problem was the price at which we get our hotels.\\
During the game, prices increased almost endlessly, and we've had our hotel nights for a very big price usually (sometimes more than 500/night).\\
However, we did not have a swap strategy, and usually we bought the good hotel for a huge price whereas the cheap one was available. However, this strategy is far more difficult to implement because a client can't change hotels during his stay.

\subsection{Entertainement}
This part of the auction went quite well.\\
As expected, we got for each game all of the entertainements we asked for, which results in a high satisfaction.\\
However, it may have append that we bought an entertainement too high for a client, and got a negative score for it. Our strategy was good but could still be improved.\\
As for the other side of our strategy, we've seen very little effects : the other agents did not seem to suffer from the starvation we tried to induce.

\subsection{General}
As we've seen, the main problem with our strategies was the price. We had one of the highest satisfaction score in each game, but ended up with a negative result because we bought hotels and entertainements too expensive.\\
However, this behaviour was a risk we were willing to take, so the real problem according to us is the hotel nights we couldn't get, which was a real hard hit.
